Delocalization of Eigenvectors in Random Matrices

### 2025-03-21 Draft.tex
g31

\noindent Let us start by bounding the loop at $\delta$, as well as the $x\textcolor{red}{\rightarrow}y$, $\beta\textcolor{blue}{\rightarrow}\alpha$ and $\alpha\textcolor{blue}{\rightarrow}\gamma$. In totality, this contributes $O(W^{-2}\eta_s^{-1})$. Here, however, we don't have the same structure as before, since $\gamma$ no longer has an ingoing edge from $x$. Regardless, observe that by preserving $x\textcolor{blue}{\rightarrow}\beta$, when we are performing the total estimation at the end, the wavy lines will be contributing only with $O(1)$ per estimate $(5)$, hence we can expect for the result to be equivalent to the two prior two : $\mathcal{G}_{31, s}\lesssim W^{-2}\eta_s^{-1}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (beta) at (2, 0) {$\beta$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

>>>>

\noindent Let us start by bounding the loop at $\delta$, as well as the $x\textcolor{red}{\rightarrow}y$, $\beta\textcolor{blue}{\rightarrow}\alpha$ and $\alpha\textcolor{blue}{\rightarrow}\gamma$. In total, this contributes $O(W^{\delta_\sto/5}W^{-2}\eta_s^{-1})$. However, here we don't have the same structure as before, since $\gamma$ no longer has an ingoing edge from $x$. Regardless, observe that by preserving $x\textcolor{blue}{\rightarrow}\beta$, when we are performing the total estimation at the end, the wavy lines will be contributing only with $O(1)$ per estimate $(5)$, hence we can expect for the result to be equivalent to the two prior two : $\mathcal{G}_{31, s}\lesssim W^{\delta_\sto/5} W^{-2}\eta_s^{-1}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (beta) at (2, 0) {$\beta$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};
